\section{Conclusion}
This work introduced an algorithm designed to support the learning and teaching of ND, with the aim of generating high-quality educational feedback. Through the construction of graphs based on labeled directed hypergraphs, the system is able to automatically generate complete, human-readable ND proofs and explore multiple proof paths for a given problem.

The main contributions of this work are:
\begin{itemize}
    \item A method for generating multiple valid ND proofs for both PL and FOL.
    \item An efficient feedback mechanism that aligns with the student’s reasoning, rather than enforcing a single rigid solution path.
    \item A way to quantify progress, offering metrics such as distance to a valid proof and detection of redundant or more complex steps.
\end{itemize}

Furthermore, the algorithm has the potential to generate exercises with specified difficulty levels, and exploring this capability is planned as part of future work.

Unlike previous methods, our algorithm not only returns a single best solution but also provides step-by-step feedback that aligns with the student’s problem-solving process, enhancing its educational value. Additionally, it stores multiple solutions in advance, making real-time feedback efficient and scalable.

The algorithm is fully implemented and is being integrated into an online learning platform. We expect it to have immediate impact in classroom and self-study settings, helping students better understand ND and teachers to evaluate student solutions more effectively.